---
title: |
  \begin{center}
  {\Large \textbf{ALMA MATER STUDIORUM – UNIVERSITA’ DI BOLOGNA}}\\[1.5cm]
  {\large DIPARTIMENTO DI SCIENZE STATISTICHE}\\
  {\large “PAOLO FORTUNATI”}\\[2cm]
  {\large Corso di Laurea in Scienze Statistiche}\\[2cm]
  \end{center}
  \vfill
  \begin{center}
  {\Huge \textbf{TITOLO}}\\[0.5cm]
  {\Large (Materia)}
  \end{center}
  \vfill
author: "Lucrezia Galli"
date: "2025-02-20"
format: 
  pdf:
    number-sections: true  # Enables section numbering
bibliography: biblio.bib  # Link the BibTeX file
header-includes: |
  % Set Arial font globally
  \usepackage{helvet}  
  \renewcommand{\familydefault}{\sfdefault}  


  % Ensure correct document structure
  \usepackage{titling}
  \usepackage{array}
  \usepackage{ragged2e}

  % Define Presentata and Appello sections
  \newcommand{\presentata}{%
    \begin{flushleft}
    \begin{tabular}{ p{7cm} p{7cm} }
    \textbf{Presentata da:} & \hfill \textbf{Relatore:} \\
    Nome e Cognome & \hfill Prof … … \\
    Matricola: … … &  \\
    \end{tabular}
    \end{flushleft}
  }
  \newcommand{\appello}{%
    \vfill
    \begin{center}
    \textbf{APPELLO … …}\\[0.5cm]
    \textbf{ANNO ACCADEMICO … / …}
    \end{center}
  }
---
```{r}
source("C:/Users/luca galli/OneDrive/Documenti/lucrezia secondo anno/utilizzo banche dati/pacchetti.R")
```
 

```{r}
ifpack(c("sf", "terra", "spData", "rnaturalearth", "rnaturalearthdata", "tmap", "wbstats", "tidyverse", "devtools", "httr", "Statamarkdown", "reticulate", "ggplot2", "dplyr", "viridis", "geometry", "jsonlite", "WDI", "worldbank", "countrycode"))
poverty<-wb_search("poverty")
poverty

```


\presentata

\appello

\newpage  

\fontsize{12pt}{14pt} \selectfont  

# Introduction

This study is based on statistical analysis methods presented by Smith [@smith2020] and recent developments in data science discussed by Jones and Brown [@jones2018].

# Machine Learning in Healthcare

Lee and White [@lee2019] highlighted key advancements in AI-driven healthcare, while Williams [@williams2021] examined societal impacts of big data.

# Online Resources

For a general understanding of statistical learning, see Doe’s online guide [@doe2023].

# Conclusions

# References